Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = "\t")

qplot(x = age, y =friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response:

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point() +
  xlim(13,90)

summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) +
  xlim(13,90)

```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) +
  xlim(13,90) +
  coord_trans(y = "sqrt")

```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20, position = position_jitter(h = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")
```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/10, position = position_jitter(h = 0)) +
  xlim(13,90) +
  coord_trans(y = "sqrt")

```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)

age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_median = median(friend_count),
          n = n())

pf.fc_by_age <-arrange(pf.fc_by_age, age)
head(pf.fc_by_age)

pf.fc_by_age2 = pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)
head(pf.fc_by_age2, 20)
```

Create your plot!

```{r Conditional Means Plot}
ggplot(pf.fc_by_age, aes(age, friend_count_mean)) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20,
             position = position_jitter(h = 0),
             color = 'orange') +
  xlim(13,90) +
  coord_trans(y = "sqrt") +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .1),
            linetype = 2, color = "blue") +
    geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .5),
            color = "blue") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .9),
            linetype = 2, color = "red")

ggplot(aes(x = age, y = friend_count), data = pf) + 
  coord_cartesian(xlim = c(13, 70), ylim = c(0, 1000)) +
  geom_point(alpha = 0.05,
             position = position_jitter(h = 0),
             color = 'orange') +
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .1),
            linetype = 2, color = "blue") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .5),
            color = "blue") +
  geom_line(stat = 'summary', fun.y = quantile, fun.args = list(probs = .9),
            linetype = 2, color = "red")

```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor.test(pf$age, pf$friend_count, method="pearson")

```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf, age <= 70) , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

with(subset(pf, age <= 70) , cor.test(age, friend_count), method = "")

***

## Create Scatterplots
Notes:

```{r}
ggplot(pf, aes(www_likes_received, likes_received)) +
  geom_point()

ggplot(pf, aes(friend_count, likes_received)) +
  geom_point()

ggplot(pf, aes(age, likes_received)) +
  geom_point()

ggplot(pf, aes(www_likes_received, likes_received)) +
  geom_point() +
  xlim(0, quantile(pf$www_likes_received, 0.95)) +
  ylim(0, quantile(pf$likes_received, 0.95)) +
  geom_smooth(method = "lm", color="red")

```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
cor.test(pf$www_likes_received, pf$likes_received)
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data(Mitchell)
names(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
  geom_point() +
  geom_smooth(method = "lm", color="red")
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.
0
b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month, Mitchell$Temp)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
range(Mitchell$Month)
ggplot(data = Mitchell, aes(x = Month, y = Temp)) +
  geom_point() +
  scale_x_continuous(breaks=seq(0,203,12))

ggplot(aes(x=(Month%%12),y=Temp),data=Mitchell)+ 
  geom_point()

x <- seq(0, 4*pi, pi/20)
y <- cos(x)
qplot(x = x, y = y)
dcor.ttest(x, y)

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(data = pf.fc_by_age, aes(x = age, y = friend_count_mean)) +
  geom_line()

pf$age_with_months <- pf$age + (12 - pf$dob_month) / 12
range(pf$age_with_months)
```

***

### Age with Months Means

```{r Age with Months Means}
pf.fc_by_age_months = pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)
summary(pf.fc_by_age_months)
head(pf.fc_by_age_months)
```

Programming Assignment
```{r Programming Assignment}
ggplot(data = pf.fc_by_age_months, aes(x = age_with_months, y = friend_count_mean)) +
  geom_point() +
  xlim(0,71)
  
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(data = subset(pf.fc_by_age_months, age_with_months < 71),
       aes(x = age_with_months, y = friend_count_mean)) +
  geom_line()
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}

```
ggplot(data = subset(pf.fc_by_age_months, age_with_months < 71),
       aes(x = age_with_months, y = friend_count_mean)) +
  geom_line() +
  geom_smooth()
***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

